Association between trauma severity models and opportunities for improvement:

### 2022-11-02 manuscript.Rmd
fixed method more

<!-- Clearly define all outcomes, exposures, predictors, potential
confounders, and effect modifiers. Give diagnostic criteria, if
applicable. For each variable of interest, give sources of data and
details of methods of assessment (measurement). Describe comparability
of assessment methods if there is more than one group -->

@@

The PS model incorporates patient age, gender, GCS and ISS.

@@

<!-- Describe any efforts to address potential sources of bias -->

The method and data analysis model will be written using simulated data to reduce the risk of research bias. Real-world data will only be used once the data analysis model is completed and found to work correctly on simulated data.

Study size 
----------

<!-- Explain how the study size was arrived at -->

Since all eligible participants must exist in both the trauma registry and the trauma care quality database, and the trauma care quality database is a subset of the trauma registry, the maximum number of participants is limited to the number of cases registered in the trauma care quality database. The trauma care quality database includes around 2200 patients who were selected for review between 2014 and 2021. In order to establish the exact study size, the study-specific exclusion criteria need to first be applied. The exact study size has not yet been established at the time of writing this report.

RTS, NORMIT and PS12 were calculated according to the published algorithms from their developers [@rtsalgorithm, @normit, @psalgorithm]. TRISS was calculated using to the revised 2009 coefficients [@triss2010].

>>>>

@@

The algorithm for PS includes the patient's age, gender, GCS and ISS.

RTS, NORMIT and PS12 were calculated according to the original published algorithms [@rtsalgorithm, @normit, @psalgorithm]. TRISS was calculated using the revised 2009 coefficients [@triss2010].

@@

The code for data analysis was written using simulated data to reduce the risk of research bias. Real-world data was only used once the data analysis model was completed and found to work correctly on simulated data.
